Sound Automated Synthesis of Digital Controllers

### 2016-10-10 paper/paper.tex
Changes on 2.1.

\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}

@@

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is sufficiently
equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
function $G(s)$ driven by ZOH.  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

@@

\begin{myassumption}
%
The controller and the plant are linear, {\it i.e.}, any source of
nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
be disregarded.
%
\end{myassumption}

>>>>

%\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}

@@

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
function $G(s)$ driven by ZOH.  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

\begin{myassumption}
%
The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
be disregarded. Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  may be considered a sufficient discrete-time representation of $G(s)$.
%
\end{myassumption}

@@
